Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Describe verifiable counting in Helios

>>>>

In some ways, count verification is simpler than that in Scantegrity. We have already discussed how
Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this mechanism,
they are decrypted, and so the actual plaintext ballots are exposed. From that point, tallying is
straightforward.
